---
title: "W01-27-Inferfaces to the Outside World"
author: "Lluis Calvo"
date: "1/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Interfaces to the Outside World

Data are read in using connection interfaces. Connections can be made to files (most common) or to other more exotic things.
* file, opens a connection to a file  
* gzfile, opens a connection to a file compressed with gzip  
* bzfile, opens a connection to a file compressed with bzip2 · url, opens a connection to a webpage  

## File Connections

```{r}

str(file)

```



* Description is the name of the file
* Open is a code indicating  
  - “r”readonly  
  - “w”writing(andinitializinganewfile)  
  - “a”appending  
  - “rb”,“wb”,“ab”reading,writing,orappendinginbinarymode(Windows)  


## Connections

In general, connections are powerful tools that let you navigate files or other external objects. In practice, we often don’t need to deal with the connection interface directly.

```{r}
con <- file("W01-27-foo.txt", "r") 
data <- read.csv(con) 
close(con)

head(data)
```

is the same as
```{r}
data <- read.csv("W01-27-foo.txt")

head(data)
```

## Readling Lines of a Text File


```{r}
con <- gzfile("W01-27.gzfile.tar")

x <- readLines(con, 10)

x

```
 
 
## Reading Lines of a Text File

readLines can be useful for reading in lines of webpages

```{r}
con <- url("http://www.jhsph.edu", "r")

x <- readLines(con)

x

```

