---
title: "W01-26-Textual Data Formats"
author: "Lluis Calvo"
date: "1/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Textual Data Formats

## Textual Formats
* dumping and dputing are useful because the resulting textual format is edit-able, and in the case of corruption, potentially recoverable.  
* Unlike writing out a table or csv file, dump and dput preserve the metadata (sacrificing some readability), so that another user doesn’t have to specify it all over again.  
* Textual formats can work much better with version control programs like subversion or git which can only track changes meaningfully in text files  
* Textual formats can be longer-lived; if there is corruption somewhere in the file, it can be easier to fix the problem  
* Textual formats adhere to the “Unix philosophy”  
* Downside: The format is not very space-efficient  

## dput-ting R Objects

Another way to pass data around is by deparsing the R object with dput and reading it back in using dget.

```{r}

y <- data.frame(a = 1, b = "a")

dput(y)

dput(y, file = "y.R")
new.y <- dget("y.R")
new.y

```


## Dumping R Objects

Multiple objects can be deparsed using the dump function and read back in using source.

```{r}

x <- "foo"

y <- data.frame(a = 1, b = "a")

dump(c("x", "y"), file = "data.R")

rm(x, y)

source("data.R")

y

```

